R Notebook

### 2016-07-28 finalwriteup/trial_code_eq.rmd
finished kerrie editing

$$
\begin{aligned} 
\log(odds) &= \beta_0 + X_1\beta_1 + X_2\beta_2 \\ 
\log\left(\frac{p}{1-p}\right) &= \beta_0 + X_1\beta_1 + X_2\beta_2 \\ 
\log\left(\frac{0.5}{0.5}\right) &= \beta_0 + X_1\beta_1 + X_2\beta_2 \\ 
\log(1) &= \beta_0 + X_1\beta_1 + X_2\beta_2 \\ 
0 &= \beta_0 + X_1\beta_1 + X_2\beta_2 \\ 
X_2\beta_2 &= -\beta_0 - X_1\beta_1 \\ 
X_2 &= -\frac{\beta_0}{\nbeta_2} - X_1\frac{\beta_1}{\beta_2} \\ 
\end{aligned}
$$

$p(X_1 X_2|Y) = p(X_1|Y) \cdot p(X_2|X_1 Y)$

$\boldsymbol{w} \cdot \boldsymbol{x} + \beta_0 = 0$

where $\boldsymbol{w}$ and $\boldsymbol{x}$ are vectors with lengths corresponding to the number of explanatory variables. For two variables, $\boldsymbol{w}$ would be $\begin{pmatrix}\beta_1 \\ \beta_2\end{pmatrix}$ and $\boldsymbol{w}$ would be $\begin{pmatrix}X_1 \\ X_2\end{pmatrix}$ [@Fletcher2009]. Expanding the dot product of these two vectors gives the equation for a line:

$\beta_1 X_1 + \beta_2 X_2 + \beta_0 = 0$

>>>>

$p(ABCD) = p(C|ABD)\cdot p(A|BD) \cdot p(B|D) \cdot p(D)$

$p(ABCD) = p(C|BD)\cdot p(A|B) \cdot p(B) \cdot p(D)$
